Universal Anonymous Signatures

### 2022-09-19 prism-backend/research/gsac/relationships.tex
Updated GS-MDO and DAC appendices.
Completed in-depth pass. Some changes pending.

In the following, to showcase the generality of \UAS and \CUASGen, we reproduce
models of related schemes in the literature.
Then, we give concrete $(\fissue,\feval,\finsp)$-\CUASGen restrictions and prove
that they securely instantiate the models for the presented schemes, if the
corresponding \CUASGen restriction is a secure \UAS construction. Concretely,
we rely on the functions described in \figref{fig:func-restrictions}. Observe
that all the \fissue functions listed in \figref{fig:func-restrictions} are
\UAS-acceptable. Specifically, $\fissue^1$ and $\fissue^{\sring}$ are trivially
\UAS-acceptable (for $\rngfissue = \bin$); whereas $\fissue^{single,F,I}$ is
\UAS-acceptable if $F$ is a secure PRF \cite{kl14}.

\begin{figure}[ht!]
  \input{figures/functions.tex}
  \caption{Functions for the \CUASGen restrictions described next.
    For readability, we use ``$\cdot$'' to denote input arguments that are
    ignored; and ``$\ast$'' to denote output values that can be set to anything
    (but should be ignored). $\bot$ means that the function fails.}
  \label{fig:func-restrictions}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.45\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,gs}(1^\secpar)$}{%
        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
        d \gets \adv^{\mathcal{O}_{anon}}(\gpk,\isk) \\
        \pcreturn d 
      }

@@

      \procedure[linenumbering]{$\Exp^{frame}_{\adv,gs}(1^\secpar)$}{%
        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}_{frame}}
        (\gpk,\osk,\isk) \\
        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
        \pcreturn (\upk \in \HU \land \PRVUK[\upk] \neq \bot \land
        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1)~\land \\
        \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
        GSig(\PRVUK[\upk],\msg)
      }       
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.55\textwidth}
      \procedure[linenumbering]{$\Exp^{trace}_{\adv,gs}(1^\secpar)$}{%
        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
        (\msg,\sig) \gets \adv^{\mathcal{O}_{trace}}(\gpk,\osk) \\
        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
        (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
        \pcif \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
        = 0: \\ 
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for group signatures \cite{bsz05}, only with minor    
    ``harmless'' edits to compare easier with \CUASGS. Concretely, since we
    output {\upk}s instead of indexes, $i=0$ in the traceability game now reads
    $\upk \notin \HU \cup \CU$. For the oracles' definitions, check the
    referenced paper.
    $\mathcal{O}_{anon} \gets \lbrace \oracle{Ch},\oracle{Open},\oracle{SndToU},
    \oracle{WReg},\oracle{USK},\oracle{CrptU} \rbrace$,
    $\mathcal{O}_{trace} \gets \lbrace \oracle{SndToI},\oracle{AddU},
    \oracle{RReg},\oracle{GSig},\oracle{USK},\oracle{CrptU} \rbrace$,
    and $\mathcal{O}_{frame} \gets \lbrace \oracle{SndToU},\oracle{WReg},
    \oracle{GSig},\oracle{USK},\oracle{CrptU} \rbrace$.
  }
  \label{fig:model-gs}  
\end{figure}

\subsubsection{\CUASGS construction.} %
We show that the $(\fissue^{single,F,I},\feval^0,\finsp^{\upk})$-\CUASGen
restriction, is a secure group signature scheme according to \cite{bsz05}.
As stated, the $\fissue^{single,F,I}$ is an \UAS-acceptable function if $F$ is a
PRF. In that case, its output is a random-looking string that depends on the
user public key \upk, and a string $I$ uniquely identifying the issuer. Thus, it
will be the same per $(\upk,I)$ pair, and can be used by issuer $I$ to prevent
issuing more than one credential per user. Basically, the issuer maintains a
list of received $\yissue = F(\upk,I)$ values, and rejects issuing a credential
for already existing \yissue values. From this, the GS algorithms are as
follows:

\begin{description}
\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs \Setup from \CUASGen,
  and one instance of \KeyGen and \ISet with $\fissue^{single,F,I}$ (both for
  the same user, who will be the only issuer in the GS scheme) and \OKeyGen.
  Assigns the public keys to \gpk.
\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \KeyGen from \CUASGen.
\item[$\langle \cred,\utrans \rangle \gets
  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$. Upon receiving
  the \yissue value, the issuer checks if it already exists in a list $L$
  (initially set to $\emptyset$); if it exists, aborts issuance. Otherwise, it
  completes the protocol and adds $\yissue$ to $L$. It is responsibility of the
  issuer to maintain $L$.
\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen,
  where $\yeval = 0$ is the constant output of $\feval^0$.
\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  returns whatever $\Verify(\opk,\ipk,\sig,0,\msg,\feval^0)$ from \CUASGen
  outputs.
\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Parses \gpk as
  $(\ipk,\opk)$, and returns whatever \CUASGen outputs in $\Open(\osk,\ipk,\sig,
  0,\msg,\feval^0)$. Internally, the call to \Open runs $\finsp^{\upk}$.
\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Parses \gpk as $(\ipk,
  \opk)$, and returns whatever \CUASGen outputs in $\Judge(\opk,\upk,\pi,\sig,
  0,\msg)$.
\end{description}

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.55\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rs}(1^\secpar)$}{%
        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
        (i_0,i_1,R,\msg,\st) \gets \adv^{\oracle{SIGN}}(\pk_1,\dots,\pk_n) \\
        \pcif R \not\subseteq \lbrace \pk_i \rbrace_{i\in[n]} \lor
        \lbrace \pk_{i_0},\pk_{i_1} \rbrace \not\subseteq R~\lor \\ %\\
        \pcind i_0 = i_1: \pcreturn \bot \\
        \sig \gets Sign(\sk_{i_b},R,\msg) \\
        b^* \gets \adv(\sig,\st) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rs}(1^\secpar)$}{%
        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
        (R,\sig,\msg) \gets \adv^{\oracle{SIGN},\oracle{CORR}}
        (\pk_1,\dots,\pk_n) \\
        \pcif Verify(R,\sig,\msg) = 0: \pcreturn 0 \\
        \pcreturn (R \subseteq \lbrace \pk_i \rbrace_{i\in[n]} \setminus
        CU~\land \\
        \pcind \adv~\textrm{never queried}~SIGN(\cdot,R,\msg))
      }       
    \end{minipage}      
  }
  \caption{Security games for ring signatures \cite{bkm06}. The $\oracle{SIGN}$
    oracle accepts $(i,R,\msg)$ tuples, with $pk_i \in R$, adds the tuple to a
    list of queries, and returns $\sig \gets Sign(\sk_i,R,\msg)$.
    $\oracle{CORR}$ accepts an index $i$, and leaks $\sk_i$. Corrupted users are
    added to $CU$.}
  \label{fig:model-rs}  
\end{figure}

\subsubsection{\CUASRing Construction.} %
Building a ring signature scheme according to the model in \figref{fig:model-rs}
is essentially a $(\fissue^{\sring},\feval^{\sring,\dattrs},\finsp^0)$-restriction
of our \CUASGenHideIss construction. In a nutshell, we let users self-issue
credentials where the attributes are (a subset of encodings of) the public keys
of the users in the system -- including their own public key. Then, a ring
signature is just a \CUASGenHideIss signature that reveals a subset of
the attributes -- i.e., a subset of the keys of the users in the system. In more
detail, the construction is as follows:

@@

\begin{description}
%\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in \CUASGenHideIss.
\item[$((\pk_1,\sk_1),...,(\pk_n,\sk_n)) \gets KeyGen(\secpar)$.] Runs
  $\parm \gets \Setup(\secpar)$ from \CUASGenHideIss. Then, for each of
  the $i \in [n]$ users to generate, run $(\upk_i,\usk_i) \gets \KeyGen(\parm)$,
  and $\ipk_i \gets \ISet((\upk_i,\usk_i),\fissue^{\sring})$, where $\sring =
  \lbrace \upk_i \rbrace_{i\in[n]}$. Run also $(\opk,\osk) \gets \OKeyGen(\parm,
  \finsp^0)$. Set $\pk_i \gets (\ipk_i,\opk)$ and $\sk_i \gets \usk_i$, for
  $i\in[n]$.
\item[$\Sig \gets \Sign(\sk_i,R,\msg).$]
  The signing user, with $\sk_i=\usk$ and $\pk_i=(\ipk_i,\opk)$ for some $i \in
  [n]$, where $\pk_i \in R$, first acts both as user and issuer to self-issue a
  credential \Cred over an attribute set \attrs such that $\attrs \subseteq
  \sring$. The user picks some \dattrs such that $\dattrs \subseteq [|\attrs|]$,
  and computes the ring signature by running $\Sig = (\sig,\yeval) \gets
  \Sign(\usk,\opk,\Cred,\msg,\feval^{\sring,\dattrs})$ from
  \CUASGenHideIss. Note that \dattrs defines the public keys within
  $\attrs \subseteq \sring$ to be revealed through \yeval.
\item[$1/0 \gets Verify(R,\Sig,\msg)$.] Parses \Sig as $(\sig,\yeval)$ and
  runs $\Verify(\opk,\yeval,\Sig,\msg,\feval^{\sring,\dattrs})$ as in
  \CUASGenHideIss. Note that, in valid signatures, $\yeval = \lbrace
  \ipk_i\rbrace_{i\in\dattrs}$.
\end{description}

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.5\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
 %       \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets IssKeyGen(1^\secpar) \\        
        b^* \gets \adv^{\oracle{HU},\oracle{CU},\oracle{Obtain},
          \oracle{Show},\oracle{LoR}}(\isk) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
%        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets IssKeyGen(1^\secpar) \\        
        (D,\st) \gets \adv^{\oracle{HU},\oracle{CU},\oracle{ObtIss},
          \oracle{Issue},\oracle{Show}}(\ipk) \\
        \langle \cdot,(b,\utrans) \rangle
        \gets \langle \adv(\st),\Verify(\ipk,D) \rangle \\
        \pcreturn (b = 1 \land \nexists j~\suchthat \\
        \pcind (\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j])) % \forall j, \OWNR[j] \in \CU
        % \implies D \not\subseteq \ATTR[j]: \\
        %\pcind \pcreturn 1 \\
        %\pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Games for anonymous credentials with selective disclosure
    \cite{fhs19}. \OWNR, \ATTR, and the oracles, are essentially as in
    \UAS. \adv~wins $\Exp^{forge}_{\adv,ac}$ if it authenticates successfully
    while revealing attributes not contained in adversarially controlled
    credentials.}
  \label{fig:model-ac}  
\end{figure}

@@

\subsection{Revocable Anonymous Credentials}
\label{ssec:related-models-rac}

In \cite{cks10,ckl+15}, revocable anonymous credentials are proposed. We first
give a simple model in \figref{fig:model-rac}, extending that in
\secref{ssec:related-models-ac}. Concretely, to the functionality in
\secref{ssec:related-models-ac}, we now explicitly add the $OKeyGen$ function,
which generates the opener key pair, extend $Verify$ to receive also a list $L$
of revoked credential identifiers, and we add a function (and corresponding
oracle) $cid/\bot \gets RetrieveCredId(\osk,\utrans)$ that can extract an
identifier of the credential used in a presentation transcript \utrans. For
simplicity, we do not include the equivalent to verifiable openings, but this
would be straightforward.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.43\textwidth}
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\opk,\osk) \gets \OKeyGen(\parm) \\        
        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
        b^* \gets \adv^{\mathcal{O}_{rac},\oracle{LoR}}(\parm,\ipk,\opk) \\
        \pcreturn b^*
      }
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.57\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\opk,\osk) \gets \OKeyGen(\parm) \\        
        (\ipk,\isk) \gets IssKeyGen(\parm) \\
        (\cid,D,L,\st) \gets
        \adv^{\mathcal{O}_{rac}}(\parm,\ipk,\opk) \\
        \langle \cdot,(b_0,\utrans_0)\rangle
        \gets \langle \adv(\st),\Verify(\ipk,D,L)\rangle \\
        \langle \cdot,(b_1,\utrans_1)\rangle
        \gets \langle Show(\ipk,\ATTR[\cid],D,\CRED[\cid]), \\
        \hspace*{7.25em}\Verify(\ipk,D,L)\rangle \\
        \pcif \OWNR[\cid] \notin \HU \lor
        D \not\subseteq \ATTR[\cid]: \pcreturn 0 \\
        \pcif b_0 = 1 \land \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \\
        \pcind \pcreturn 1 \\
        h_{\bin} \gets RetrieveCredHandle(\osk,\utrans_{\bin}) \\
        \pcif h_0 \in L \lor (h_1 \notin L \land b_1 = 0): \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for revocable anonymous credentials with selective
    disclosure based on \cite{fhs19}. 
    $\mathcal{O}_{rac} \gets \lbrace \oracle{HU},\oracle{CU},\oracle{Obtain},
    \oracle{Issue},\oracle{ObtIss},\oracle{Show},\oracle{ReqCredHandle}\rbrace$.
    $\oracle{ReqCredHandle}$ is
    equivalent to \OPEN, operating on transcripts \utrans instead of signatures
    but, in addition, keeps a list of revoked users (per verifier), based on the
    queries it receives. In $\Exp^{forge}_{\adv,rac}$, \adv~wins if it
    authenticates using a revoked credential or despite not having the required
    attributes, or if it prevents an honest user from authenticating using a
    non-revoked credential.}
  \label{fig:model-rac}  
\end{figure}

\subsubsection{\CUASRAC Construction.} %
Briefly, this is achieved via a $(\fissue^1,\feval^{\dattrs,F,V,L},
\finsp^{F})$-\CUASGenInt restriction. \feval is defined via a set of
attributes \dattrs to reveal (e.g., age, etc.), a PRF $F$, a string identifying
the verifier $V$ and a list $L$ of revocation handles by $V$. Note that,
these ``extra parameters'' can be hardcoded, though: $F$ can be a fixed PRF for
all verifiers, \dattrs and $V$ are also fixed (per verifier), and $L$ can be
updated per verifier with some reasonable frequency -- e.g., daily -- so that
the cost of recomputing $\feval^{\dattrs,F,V,L}$ is not high.
%
Since credentials in \CUASGenInt have two identifiers (\cidi, chosen by the
issuer; and \cidu, chosen by the user), $\feval^{\dattrs,F,V,L}$ internally
computes $F(V,\cidi)$ and $F(V,\cidu)$. If either appears in $L$, \feval aborts.
Otherwise, it sets $\yeval^0 \gets \lbrace \attrs_i \rbrace_{i\in\dattrs}$ and
$\yeval^1 \gets V$. $\yeval^1$ is
then used by $\finsp^F$ to compute $\yinsp \gets (F(\yeval^1,\cidi),
F(\yeval^1,\cidu))$. Thus, if the verifier $V$ wants to revoke a credential, all
it has to do is ask the opener to decrypt $\yinsp$, via $RetrieveCredHandle$.
%
In more detail, the algorithms are as follows:

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\Setup(1^\secpar)$ as in
  \CUASGenInt.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \KeyGen+\ISet from
  \CUASGenInt, setting $\fissue^1$ as issuance function.
\item[$(\ipk,\isk) \gets OKeyGen(\parm)$.] Runs \OKeyGen from \CUASGenInt,
  setting $\finsp^F$ as opening function.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from \CUASGenInt.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGenInt, using
  $\fissue^1$ as issuance function.
\item[$\langle 1/0,(\yeval,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,
  \attrs,\dattrs,\cred),
  \Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive $\langle\Sign,\Verify\rangle$ of \CUASGenInt,
  using $\feval^{\dattrs,F,V,L}$ as signature evaluation function, and
  $\finsp^F$ as open function. The \yeval value output by the verifier, when
  it accepts, is the $\yeval^0$ value produced by \Sign in \CUASGenInt.
\item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
  Gets $(\sig,\yeval^0)$ from the $\langle Show,\Verify\rangle$ transcript
  \utrans, and runs \Open from \CUASGenInt. This returns $(F(V,\cidi),
  F(V,\cidu))$, which the verifier can add to its revocation list $L$.
\end{description}

\paragraph{Security of \CUASRAC.} %
Our \CUASRAC construction is an anonymous and unforgeable revocable anonymous
credential scheme, according to the model in \figref{fig:model-rac}. For space
constraints, proofs are deferred to \appref{app:related-proofs}.

% \begin{theorem}[Anonymity of \CUASRAC]
%   If the base \CUASGenInt construction has signature anonymity according to
%   \defref{def:sign-anonymity-uas}, then \CUASRAC is an anonymous AC scheme
%   according to \cite{fhs19}.  
% \end{theorem}

% \begin{theorem}[Unforgeability of \CUASRAC]
%   If the base \CUASGenInt construction is unforgeable according to
%   \defref{def:forge-uas}, and $F$ is a one-way function, then \CUASRAC is an
%   unforgeable RAC scheme.
% \end{theorem}

\subsection{Multimodal Private Signatures}
\label{ssec:related-models-mps}

Multimodal Private Signatures (or, rather, a close relative, see next) are
directly implementable as a $(\fissue^{single,F,I},\feval^{g,MPS},
\finsp^{h,MPS})$-\CUASGen restriction. Concretely, this restricts to a system
with one credential per user and no attributes in the credentials.

>>>>

In the following, to showcase the generality of \UAS and \CUASGen, we reproduce
models of related schemes in the literature.
Then, we give concrete $(\fissue,\feval,\finsp)$-\CUASGen restrictions and prove
that they securely instantiate the models for the presented schemes, if the
corresponding \CUASGen restriction is a secure \UAS construction. Concretely,
we rely on the functions described in \figref{fig:func-restrictions}. Observe
that all the \fissue functions listed in \figref{fig:func-restrictions} are
\UAS-acceptable. Specifically, $\fissue^1$ and $\fissue^{\sring}$ are trivially
\UAS-acceptable (for $\rngfissue = \bin$); whereas $\fissue^{single,H,I}$ is
\UAS-acceptable if $F$ is a secure PRF \cite{kl14}.

\begin{figure}[ht!]
  \centering
  \scalebox{0.85}{
    \input{figures/functions.tex}
  }
  \caption{Functions for the \CUASGen restrictions described next.
    For readability, we use ``$\cdot$'' to denote input arguments that are
    ignored; and ``$\ast$'' to denote output values that can be set to anything
    (but should be ignored). $\bot$ means that the function fails.}
  \label{fig:func-restrictions}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.85}{      
    \begin{minipage}[t]{0.45\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,gs}(1^\secpar)$}{%
        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
        d \gets \adv^{\mathcal{O}_{anon}}(\gpk,\isk) \\
        \pcreturn d 
      }

@@

      \procedure[linenumbering]{$\Exp^{frame}_{\adv,gs}(1^\secpar)$}{%
        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}_{frame}}
        (\gpk,\osk,\isk) \\
        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
        \pcreturn \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
        \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
        GSig(\PRVUK[\upk],\msg)
      }       
    \end{minipage}
  }
  \scalebox{0.85}{      
    \begin{minipage}[t]{.55\textwidth}
      \procedure[linenumbering]{$\Exp^{trace}_{\adv,gs}(1^\secpar)$}{%
        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
        (\msg,\sig) \gets \adv^{\mathcal{O}_{trace}}(\gpk,\osk) \\
        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
        (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
        \pcreturn \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
        = 0
      }       
    \end{minipage}      
  }
  \caption{Security games for group signatures \cite{bsz05}, only with minor    
    ``harmless'' edits to compare easier with \CUASGS. Concretely, since we
    output {\upk}s instead of indexes, $i=0$ in the traceability game now reads
    $\upk \notin \HU \cup \CU$. For the oracles' definitions, check the
    referenced paper.
    $\mathcal{O}_{anon} \gets \lbrace \oracle{Ch},\oracle{Open},\oracle{SndToU},
    \oracle{WReg},\oracle{USK},\oracle{CrptU} \rbrace$,
    $\mathcal{O}_{trace} \gets \lbrace \oracle{SndToI},\oracle{AddU},
    \oracle{RReg},\oracle{GSig},\oracle{USK},\oracle{CrptU} \rbrace$,
    and $\mathcal{O}_{frame} \gets \lbrace \oracle{SndToU},\oracle{WReg},
    \oracle{GSig},\oracle{USK},\oracle{CrptU} \rbrace$.
  }
  \label{fig:model-gs}  
\end{figure}

\subsubsection{\CUASGS construction.} %
We show that the $(\fissue^{single,H,I},\feval^0,\finsp^{\upk})$-\CUASGen
restriction, is a secure group signature scheme according to \cite{bsz05}.
As stated, $\fissue^{single,H,I}$ is an \UAS-acceptable function if $F$ is a
PRF. In that case, its output is a random-looking string that depends on the
user public key \upk, and a string $I$ uniquely identifying the issuer. Thus, it
will be the same per $(\upk,I)$ pair, and can be used by issuer $I$ to prevent
issuing more than one credential per user. Basically, the issuer maintains a
list of received $\yissue = F(\upk,I)$ values, and rejects issuing a credential
for already existing ones. From this, the GS algorithms are as
follows:

\begin{description}
\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs \Setup from \CUASGen,
  and one instance of \KeyGen and \ISet with $\fissue^{single,H,I}$ (both for
  the same user, who will be the only issuer in the GS scheme) and \OKeyGen.
  Assigns the public keys to \gpk.
\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \KeyGen from \CUASGen.
\item[$\langle \cred,\utrans \rangle \gets
  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$. Upon receiving
  the \yissue value, the issuer checks if it already exists in a list $L$
  (initially set to $\emptyset$); if it exists, aborts issuance. Otherwise, it
  completes the protocol and adds $\yissue$ to $L$. It is responsibility of the
  issuer to maintain $L$.
\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen,
  where $\yeval = 0$ is the constant output of $\feval^0$.
\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  returns whatever $\Verify(\opk,\ipk,\sig,0,\msg,\feval^0)$ from \CUASGen
  outputs.
\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Parses \gpk as
  $(\ipk,\opk)$, and returns whatever \CUASGen outputs in $\Open(\osk,\ipk,\sig,
  0,\msg,\feval^0)$. Internally, the call to \Open runs $\finsp^{\upk}$.
\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Parses \gpk as $(\ipk,
  \opk)$, and returns whatever \CUASGen outputs in $\Judge(\opk,\upk,\pi,\sig,
  0,\msg)$.
\end{description}

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.85}{      
    \begin{minipage}[t]{0.55\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rs}(1^\secpar)$}{%
        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
        (i_0,i_1,R,\msg,\st) \gets \adv^{\oracle{SIGN}}(\pk_1,\dots,\pk_n) \\
        \pcif R \not\subseteq \lbrace \pk_i \rbrace_{i\in[n]} \lor
        \lbrace \pk_{i_0},\pk_{i_1} \rbrace \not\subseteq R~\lor \\ %\\
        \pcind i_0 = i_1: \pcreturn \bot \\
        \sig \gets Sign(\sk_{i_b},R,\msg) \\
        b^* \gets \adv(\sig,\st) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.85}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rs}(1^\secpar)$}{%
        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
        (R,\sig,\msg) \gets \adv^{\oracle{SIGN},\oracle{CORR}}
        (\pk_1,\dots,\pk_n) \\
        \pcif Verify(R,\sig,\msg) = 0: \pcreturn 0 \\
        \pcreturn (R \subseteq \lbrace \pk_i \rbrace_{i\in[n]} \setminus
        CU~\land \\
        \pcind \adv~\textrm{never queried}~SIGN(\cdot,R,\msg))
      }       
    \end{minipage}      
  }
  \caption{Security games for ring signatures \cite{bkm06}. The $\oracle{SIGN}$
    oracle accepts $(i,R,\msg)$ tuples, with $pk_i \in R$, adds the tuple to a
    list of queries, and returns $\sig \gets Sign(\sk_i,R,\msg)$.
    $\oracle{CORR}$ accepts an index $i$, and leaks $\sk_i$. Corrupted users are
    added to $CU$.}
  \label{fig:model-rs}  
\end{figure}

\subsubsection{\CUASRing Construction.} %
We can use a $(\fissue^{\sring},\feval^{\sring,\dattrs},\finsp^0)$-restriction
of \CUASGenHideIss to build a ring signature scheme according to the model
in \figref{fig:model-rs}. In a nutshell, we let users self-issue
credentials where the attributes are (a subset of encodings of) the public keys
of the users in the system -- including their own public key. Then, a ring
signature is just a \CUASGenHideIss signature that reveals a subset of
the attributes -- i.e., a subset of the keys of the users in the system. In more
detail, the construction is as follows:

@@

\begin{description}
%\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in \CUASGenHideIss.
\item[$((\pk_1,\sk_1),...,(\pk_n,\sk_n)) \gets KeyGen(\secpar)$.] Runs
  $\parm \gets \Setup(\secpar)$ from \CUASGenHideIss. For each of
  the $i \in [n]$ users to generate, run $(\upk_i,\usk_i) \gets \KeyGen(\parm)$,
  and $\ipk_i \gets \ISet((\upk_i,\usk_i),\fissue^{\sring})$, where $\sring =
  \lbrace \upk_i \rbrace_{i\in[n]}$. Run also $(\opk,\osk) \gets \OKeyGen(\parm,
  \finsp^0)$. Set $\pk_i \gets (\ipk_i,\opk)$ and $\sk_i \gets \usk_i$, for
  $i\in[n]$.
\item[$\Sig \gets \Sign(\sk_i,R,\msg).$]
  The signing user, with $\sk_i=\usk$ and $\pk_i=(\ipk_i,\opk)$ for some $i \in
  [n]$ where $\pk_i \in R$, first acts both as user and issuer to self-issue a
  credential \Cred over an attribute set \attrs such that $\attrs \subseteq
  \sring$. The user picks some \dattrs such that $\dattrs \subseteq [|\attrs|]$,
  and computes the ring signature by running $\Sig = (\sig,\yeval) \gets
  \Sign(\usk,\opk,\Cred,\msg,\feval^{\sring,\dattrs})$ from
  \CUASGenHideIss. Note that \dattrs defines the public keys within
  $\attrs \subseteq \sring$ to be revealed through \yeval.
\item[$1/0 \gets Verify(R,\Sig,\msg)$.] Parses \Sig as $(\sig,\yeval)$ and
  runs $\Verify(\opk,\yeval,\Sig,\msg,\feval^{\sring,\dattrs})$ as in
  \CUASGenHideIss. Note that, in valid signatures, $\yeval = \lbrace
  \ipk_i\rbrace_{i\in\dattrs}$.
\end{description}

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.85}{      
    \begin{minipage}[t]{0.5\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
 %       \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets IssKeyGen(1^\secpar) \\        
        b^* \gets \adv^{\oracle{HU},\oracle{CU},\oracle{Obtain},
          \oracle{Show},\oracle{LoR}}(\isk) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.85}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
%        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets IssKeyGen(1^\secpar) \\        
        (D,\st) \gets \adv^{\oracle{HU},\oracle{CU},\oracle{ObtIss},
          \oracle{Issue},\oracle{Show}}(\ipk) \\
        \langle \cdot,(b,\utrans) \rangle
        \gets \langle \adv(\st),\Verify(\ipk,D) \rangle \\
        \pcreturn (b = 1 \land \nexists j~\suchthat \\
        \pcind (\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j])) % \forall j, \OWNR[j] \in \CU
        % \implies D \not\subseteq \ATTR[j]: \\
        %\pcind \pcreturn 1 \\
        %\pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Games for anonymous credentials with selective disclosure
    \cite{fhs19}. \OWNR, \ATTR, and the oracles, are essentially as in
    \UAS. \adv~wins $\Exp^{forge}_{\adv,ac}$ if it authenticates successfully
    while revealing attributes not contained in adversarially controlled
    credentials.}
  \label{fig:model-ac}  
\end{figure}

@@
